Заготовка для стилей

### 2020-06-19 Article.Rmd
Update bibliography, add custom template for odt, add references in English (as a separate file)

  en: "*Keywords:* specially protected natural territories, categories, governance types, comparison of categories, federalism, regional legislation, duplication, statistical analysis, empirical legal studies."
udk_code: "УДК 349.6"
output:
  odt_document:
    reference_odt: reference-styles.odt
    template: template.opendocument
bibliography: rcats_references.bib
csl: antinomii.csl
notes-after-punctuation: false
---

>>>>

  en: "*Keywords:* specially protected natural territories, categories, governance types, comparison of categories, federalism, regional legislation, duplication, statistical analysis, empirical legal studies."
udk_code: "УДК 349.6"
output:
  odt_document:
    reference_odt: reference-styles.odt
    template: template.opendocument
bibliography: rcats_references.bib
csl: antinomii.csl
notes-after-punctuation: false
reference-section-title: "Библиографический список"
---
